An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/sec_preliminaries.tex
Updated preliminaries

A Petri net $P$ satisfies a property $P$ (denoted by $N \models P$)
iff for all reachable markings $M_0 \xrightarrow{\sigma} M$
$M \models P$ holds.

\iffalse
\begin{verbatim}
 Examples:
  x + y < 0
  x + y < 0 \\and x + z > 0
  x + y < 0 \\or  x + z > 0

 ~P = (x + y <  0 \\and x + z >  0) \\or  x + z >  0
  P = (x + y >= 0 \\or  x + z <= 0) \\and x + z <= 0
\end{verbatim}
\fi

>>>>

A Petri net $N$ satisfies a property $P$ (denoted by $N \models P$)
iff for all reachable markings $M_0 \xrightarrow{\sigma} M$
$M \models P$ holds.

An invariant $I$ of a Petri net $N$ is a property such that $N$ satisfies $I$.
The invariant $I$ is inductive iff for all markings
$M$, if $M \models I$ and $M \xrightarrow{t} M'$ for some $t$, then
$M' \models I$.

A trap is a set of places $S \subseteq P$ such that $\post{S} \subseteq \pre{S}$.
If a trap $S$ is marked in $M_0$, i.e. $\sum_{p \in S} M_0(p) > 0$, then it is also marked in all reachable markings.
